---
title: "More Data Wrangling and Join Tables"
author: "Bastola"
date: "`r format(Sys.Date(), ' %B %d %Y')`"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      collapse = TRUE, 
                      comment=NA, 
                      warning = FALSE,
                      message = FALSE,
                      fig.height = 4, fig.width = 6, fig.align='center')


library(ggplot2)
library(ggthemes)
library(dplyr)
library(tibble)
library(purrr) 
library(tidyverse) 
```


```{r}
artists <- tibble(first = c("Jimmy", "George", "Mick", "Tom", "Davy", "John",
                            "Paul", "Jimmy", "Joe", "Elvis", "Keith", "Paul", 
                            "Ringo", "Joe", "Brian", "Nancy"), 
                  last = c("Buffett", "Harrison", "Jagger", "Jones", "Jones", 
                           "Lennon", "McCartney", "Page", "Perry", "Presley",
                           "Richards", "Simon", "Starr", "Walsh", "Wilson", "Wilson"), 
                  instrument = c("Guitar", "Guitar", "Vocals", "Vocals", "Vocals",
                                 "Guitar", "Bass", "Guitar", "Guitar", "Vocals", "Guitar", 
                                 "Guitar", "Drums", "Guitar", "Vocals", "Vocals"))


bands <- tibble(first = c("John", "John Paul", "Jimmy", "Robert", "George", "John", 
                          "Paul", "Ringo", "Jimmy", "Mick", "Keith", "Charlie", "Ronnie"), 
                last = c("Bonham", "Jones", "Page", "Plant", "Harrison", "Lennon",
                         "McCartney", "Starr", "Buffett", "Jagger", "Richards", "Watts", "Wood"), 
                band = c("Led Zeppelin", "Led Zeppelin", "Led Zeppelin", "Led Zeppelin",
                         "The Beatles", "The Beatles", "The Beatles", "The Beatles",
                         "The Coral Reefers", "The Rolling Stones", "The Rolling Stones",
                         "The Rolling Stones", "The Rolling Stones"))

```


## Your Turn 1

```{r}
glimpse(artists)
glimpse(bands)
```

### a. Use `left_join()` to join artists to bands.

```{r}
bands2 <- left_join(_____,_____, by = c("first", "last"))

```

### b. Use `right`_join()` to join bands to artists.

```{r}
bands3 <- right_join(_____, ______, by = c("first", "last"))
```

### c. Use `setequal()` to check that the datasets are the same.

```{r}

```


------------------------------------------------------


```{r}
albums <- tibble(album = c("A Hard Day's Night", "Magical Mystery Tour", "Beggar's Banquet",
                           "Abbey Road", "Led Zeppelin IV", "The Dark Side of the Moon", "Aerosmith",
                           "Rumours", "Hotel California"),
                 band = c("The Beatles", "The Beatles", "The Rolling Stones", "The Beatles", 
                          "Led Zeppelin", "Pink Floyd", "Aerosmith", "Fleetwood Mac", "Eagles"), 
                 year = c(1964,1967,1968,1969,1971,1973,1973,1977,1982))


songs <- tibble(song = c("Come Together", "Dream On", "Hello, Goodbye", "It's Not Unusual"),
                album  = c("Abbey Road", "Aerosmith", "Magical Mystery Tour", "Along Came Jones"), 
                first = c("John", "Steven", "Paul", "Tom"), 
                last = c("Lennon", "Tyler", "McCartney", "Jones"))


labels <- tibble(album = c("Abbey Road", "A Hard Days Night", "Magical Mystery Tour",
                           "Led Zeppelin IV", "The Dark Side of the Moon", "Hotel California", 
                           "Rumours", "Aerosmith", "Beggar's Banquet"), 
                 label = c("Apple", "Parlophone", "Parlophone", "Atlantic", "Harvest",
                           "Asylum", "Warner Brothers", "Columbia", "Decca"))
                       

```


```{r}
glimpse(albums)
glimpse(songs)
glimpse(labels)
```


## Your Turn 2

### a. Use `inner_join()` to join albums to songs.

```{r}
inner_join(____, _____, by = ______)
```

### b. Use `full_join()` to join bands to artists.

```{r}
full_join(______, _____, by = ________)
```


### c. Do the above two parts using the pipe operator, `%>%`.

```{r}
______ %>% 
  full_join(______, by = ________)
```


### d. Create one table that combines all information

```{r}
artists %>% 
  full_join(_____, by = c("first", "last")) %>% 
  full_join(_____, by = c("first", "last")) %>% 
  full_join(_____, by = c("album", "band"))
```


## Your turn 3

### a. Collect artists that have songs provided.

```{r}
artists %>% 
  semi_join(____, by = c("first", "last"))
```


### b.  Collect the albums made by a band and count them using `nrow`.

```{r}

```

### c. Return rows of artists that don't have bands info. Hint use `anti_join()`.

```{r}
artists %>% 
  anti_join(___, by = c("first","last"))
```


### d. Find the rows of songs that match a row in labels and find the number of rows.

```{r}


```


